Online Classification of arXiv Papers Based on Your Preferences

### 2014-05-20 Paper.tex
Added stopwords, set arxiver date to today.

There are some additional Python files included that we used primarily for testing. For instance, {\tt getTestData.py} and {\tt LabelData.py} are scripts that call the functions that collect arXiv data and present the abstracts to acquire labels, respectively, which we place in a single script for the user. Additionally {\tt ClassifierTester.py} takes a single classifier and tests it on a grid of possible parameters to find the best values. This enables us to run tests over each algorithm, with multiple data sets from a few different users, using a set of several values for each parameter in a fairly organized manner in the script {\tt TestClassifiers.py}. Plots are also constructed in that script as well.\\

To run the tool as a user, we've included a script {\tt Arxiver.py}, which first asks for filters to draw articles including subjects and subcategories. Then it presents abstracts from a subset of those it pulled from arXiv.  As described in Section \ref{sec:theory}, it only asks for some of labels from papers that it predicts are uninteresting. As it runs, {\tt Arxiver} automatically saves the articles that the user labels as interesting.\\

An important aspect of any text classification device is the data used to construct feature vectors. There are several approaches to text classification, itself a large field of research. We take an elementary approach and use a bag-of-words model; that is, performing a word count for each distinct word in the abstract and converting that into a vector.  We normalize this vector by the total length of the abstract,  
Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and TextFeatureVector objects are created from abstracts using {\tt FeaturizeAbstracts()}. Word counts seems like a naive approach, yet the bag-of-words model is well used and often augmented with other methods. Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.   \\
All of the software used for this tool project is available at ``github.com/skwaap/fml-arxiv'' including scripts for testing.\\

@@

We tested the different online learning algorithms with sample data generated by graduate students at NYU.  Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.\\

>>>>

There are some additional Python files included that we used primarily for testing. For instance, {\tt getTestData.py} and {\tt LabelData.py} are scripts that call the functions that collect arXiv data and present the abstracts to acquire labels, respectively, which we place in a single script for the user. Additionally {\tt ClassifierTester.py} takes a single classifier and tests it on a grid of possible parameters to find the best values. This enables us to run tests over each algorithm, with multiple data sets from a few different users, using a set of several values for each parameter in a fairly organized manner in the script {\tt TestClassifiers.py}. Plots are also constructed in that script as well.

To run the tool as a user, we've included a script {\tt Arxiver.py}, which first asks for filters to draw articles including subjects and subcategories. Then it presents abstracts from a subset of those it pulled from arXiv.  As described in Section \ref{sec:theory}, it only asks for some of labels from papers that it predicts are uninteresting. As it runs, {\tt Arxiver} automatically saves the articles that the user labels as interesting.

An important aspect of any text classification device is the data used to construct feature vectors. There are several approaches to text classification, itself a large field of research. We take an elementary approach and use a bag-of-words model; that is, performing a word count for each distinct word in the abstract and converting that into a vector.  We normalize this vector by the total length of the abstract,  
Each distinct word corresponds to a different coordinate in the feature space. This ``vectorization" is defined in a class {\tt TextFeatureVector} in {\tt ArxivData.py} and TextFeatureVector objects are created from abstracts using {\tt FeaturizeAbstracts()}. Word counts seems like a naive approach, yet the bag-of-words model is well used and often augmented with other methods. Moreover implementing such a model is not terribly complicated, which makes it a useful and attractive option.

All of the software used for this tool project is available at ``github.com/skwaap/fml-arxiv'' including scripts for testing.\\

@@

We tested the different online learning algorithms with sample data generated by graduate students at NYU.  Several students were asked to use {\tt getTestData.py} and {\tt LabelData.py} to gather the abstracts from Arxiv in categories that they specified and generate labels for each entry indicating whether they would be interested in reading a paper based on the abstract.
